\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-03-21 paper/main.tex
.

As the difference in performance with different splitting schemes is
quite large, we further evaluated additional drug--target interaction
and drug--target affinity prediction methods that were trained and
evaluation on other datasets.  Following the results of MolTrans
\cite{}\todo{add}, we reevaluated DeepDTI \cite{}\todo{add}, DeepDTA
\cite{}, DeepConv-DTI \cite{} and MolTrans itself on BioSnap\todo{What
  is that? Is it described in methods?}  \cite{} over a protein split,
as shown in part (d) of Table \ref{tab:Results}\todo{check table}. The
authors of MolTrans evaluated all considered methods over the
drug--target pair and the protein split; we were able to reproduce the
results (Table \ref{tab:Results} (d))\todo{check table}, showing a
substantial difference based on the splitting scheme. We additionally
computed the $MicroAUC_p$ score for all considered methods, leading to
comparable\todo{are the datasets comparable?} scores as for the
results obtained on the Yamanishi dataset.

@@

>>>>

As the difference in performance with different splitting schemes is
quite large, we further evaluated additional drug--target interaction
and drug--target affinity prediction methods that were trained and
evaluation on other datasets.  Following the results of MolTrans
\cite{}\todo{add}, we reevaluated DeepDTI \cite{}\todo{add}, DeepDTA
\cite{}, DeepConv-DTI \cite{} and MolTrans itself on BioSnap\todo{What
  is that? Is it described in methods?}  \cite{} over a protein split,
as shown in part (d) of Table \ref{tab:Results}\todo{check table}. The
authors of MolTrans evaluated all considered methods over the
drug--target pair and the protein split; we were able to reproduce the
results (Table \ref{tab:Results} (d))\todo{check table}, showing a
substantial difference based on the splitting scheme. We additionally
computed the $MicroAUC_p$ score for all considered methods, leading to
evaluation results that are comparable\todo{are the datasets
  comparable?} to the ones obtained on the Yaminishi dataset.

@@

There are many computational methods to predict drug--target
interactions. They can broadly be grouped in two types; the first,
which we refer to as ``bottom-up'' approaches, start from molecular
information about a drug and protein and predict an interaction based
on their molecular properties; the second, which we refer to as
``top-down'' approaches, start from observable characteristics of an
organism and infer drug--target interactions as the putative molecular
mechanisms that explain these observations; many top-down approaches
follow methods similar to those used in reverse genetics \cite{}.

Another view on these two approaches is as direct and indirect ways to
predict drug--target interactions. Molecular information can be used
to directly determine whether two molecules have the ability to
interact,
